The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH; Reproduction DOI: https://doi.org/10.48152/ssrp-1wa4-dk30]

### 2024-02-15 paper/paper.qmd
One more commit with final touches

Pluralistic ignorance describes the misalignment between private and public beliefs XX. In the context of the paper by Bursztyn et.al. (2020), it illustrates the discrepancy between an individual’s private support for women working outside the home (WWOH) and their belief of public opposition. The above authors’ findings suggest that the vast majority of married men aged 18-35 underestimate societal support for female employment, despite private beliefs that align more with progressive values. This gap between private attitudes and perceived social expectations highlights the need for interventions that accurately communicate societal beliefs to bridge the divide @paper.

@@

Even though the data imported has already been cleaned, it is not in the state that can be directly used in this paper. The cleaning process will keep XX as they are relevant to replicate the targeted aspects and the following analysis. Additionally, the main experiment's raw data's sampling methodology also contains flaws. There is incongruity between what the paper claims the data to be and what the data shows. For example, although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis. The participants' highest education also ranges from a secondary degree to a doctorate degree even though the original paper claims that they sampled men with lowest college degree @paper. The secondary degree participants, however, will not be removed from the data set as they do not affect the purpose of the analysis, and further investigation on the effect of education on the support of WWOH will be conducted in @sec-results. The sample of 500 men with some removed due to empty data points and others due to attribute qualifications is quite small to be very representative of the male population in Saudi Arabia. The cleaned data will be further explored in @sec-explore.

@@

For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of 482 observations with 8 variables. 
The variables are listed and explained below:

+ age
+ education which has five different categories: Secondary, Middle, Diploma, Bachelor, Masters, Ph.D, and Post Graduates
+ outside_self refers to whether the participant supports WWOH [0,1]
+ condition2 signifies treatment group when 1 and control group when 0
+ employed_now records whether the participant is currently employed
+ college_deg is another dummy variable referring to whether the participant has a college degree
+ children refers to how many children the participant and his wife has
+ outside_wedge is the difference in the belief between how many people in the group of 30 the participant believes would support WWOH and the actual number

@@

```{r}
#| echo: false
#| label: tbl-summ
#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
summary_stats <- main_cleaned |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment"))

@@

summary_all <- main_cleaned |>
  summarize(
    Total = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)

@@

	The original experiment discovered that nearly all participants significantly underestimated the overall support of WWOH. The survey data showed that while 83% of the participants are in favour of WWOH, the average perception is that only 56% are in favour; 82% of participants underestimated the support for WWOH.

## Bias & Weaknesses
The design of this experiment may illicit response bias from participants. Within the lens of this progressive social study, the fact that participants responded to the surveys anonymously online may sway some of them to answer in ways that differed from their true beliefs. The study addresses potential limitations regarding such bias by implementing a list experiment to mitigate these concerns (Fisher, 1993). The list experiment composed of giving participants a list of topics and they were told to state how many they agreed with, but not indicate which ones those were. This method is known to reduce the effects of social desirability bias. Despite anonymity, concerns remained that participants might feel pressured to respond in socially acceptable ways. If true, the bias would have an impact on our estimand, altering the values found and depicted in @fig-time. The list experiment, providing plausible deniability, showed consistent support for women working outside the home, suggesting minimal bias impact. Additionally, comparison with the Arab Barometer's findings corroborated the study's external validity, indicating a long-standing high level of support for women working outside the home among Saudi men, thereby strengthening the study's reliability despite potential limitations.

@@

An additional online survey aimed to delve deeper into these communication dynamics, highlights the fact that discussions about women working outside the home among male friends and relatives are infrequent. This lack of discourse correlates with larger gaps in perception versus reality, suggesting that minimal conversation contributes to widespread misperceptions. This correlation might also suggest a reverse causality, where the anticipation of conservative backlash inhibits open discussions, perpetuating a cycle of pluralistic ignorance. The lack of communication may not be entirely mass media’s failure to properly portray societal beliefs. When questioned, nearly 38% of participants very rarely discuss WWOH among their male friend circles. As shown in Figure _, the topic of WWOH is not very readily discussed among peers and colleagues. We hypothesize that this behaviour will extend onto social media, further supporting the idea that the perceived lack of support for WWOH is exacerbated by simply a deficiency in attention.

## Demographic

@@

>>>>

Pluralistic ignorance describes the misalignment between private and public beliefs @pluralistic. In the context of the paper by Bursztyn et.al. (2020), it illustrates the discrepancy between an individual’s private support for women working outside the home (WWOH) and their belief of public opposition. The above authors’ findings suggest that the vast majority of married men aged 18-35 underestimate societal support for female employment, despite private beliefs that align more with progressive values. This gap between private attitudes and perceived social expectations highlights the need for interventions that accurately communicate societal beliefs to bridge the divide @paper.

@@

Even though the data imported has already been cleaned, it is not in the state that can be directly used in this paper. The cleaning process will keep 7 as they are relevant to replicate the targeted aspects and the following analysis. Additionally, the main experiment's raw data's sampling methodology also contains flaws. There is incongruity between what the paper claims the data to be and what the data shows. For example, although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis. The participants' highest education also ranges from a secondary degree to a doctorate degree even though the original paper claims that they sampled men with lowest college degree @paper. The secondary degree participants, however, will not be removed from the data set as they do not affect the purpose of the analysis, and further investigation on the effect of education on the support of WWOH will be conducted in @sec-results. The sample of 500 men with some removed due to empty data points and others due to attribute qualifications is quite small to be very representative of the male population in Saudi Arabia. The cleaned data will be further explored in @sec-explore.

@@

For the cleaned main experiment data, irrelevant variables and empty responses were also deleted. It now consists of 482 observations with 7 variables. 
The variables are listed and explained below:

+ age
+ education which has five different categories: Secondary, Middle, Diploma, Bachelor, Masters, Ph.D, and Post Graduates
+ outside_self refers to whether the participant supports WWOH [0,1]
+ condition2 signifies treatment group when 1 and control group when 0
+ employed_now records whether the participant is currently employed
+ college_deg is another dummy variable referring to whether the participant has a college degree
+ outside_wedge is the difference in the belief between how many people in the group of 30 the participant believes would support WWOH and the actual number

@@

```{r}
#| echo: false
#| label: tbl-summ
#| tbl-cap: Summary Statistics on Men Who Participated in the Main Experiment
summary_stats <- main_cleaned |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment"))

@@

summary_all <- main_cleaned |>
  summarize(
    Total = n(),
    Age = mean(age, na.rm =TRUE),
    "College" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100)

@@

The original experiment discovered that nearly all participants significantly underestimated the overall support of WWOH. The survey data showed that while 83% of the participants are in favour of WWOH, the average perception is that only 56% are in favour; 82% of participants underestimated the support for WWOH @paper.

## Bias & Weaknesses
The design of this experiment may illicit response bias from participants. Within the lens of this progressive social study, the fact that participants responded to the surveys anonymously online may sway some of them to answer in ways that differed from their true beliefs. The study addresses potential limitations regarding such bias by implementing a list experiment to mitigate these concerns. The list experiment composed of giving participants a list of topics and they were told to state how many they agreed with, but not indicate which ones those were. This method is known to reduce the effects of social desirability bias. Despite anonymity, concerns remained that participants might feel pressured to respond in socially acceptable ways. If true, the bias would have an impact on our estimand, altering the values found and depicted in @fig-time. The list experiment, providing plausible deniability, showed consistent support for women working outside the home, suggesting minimal bias impact. Additionally, comparison with the Arab Barometer's findings corroborated the study's external validity, indicating a long-standing high level of support for women working outside the home among Saudi men, thereby strengthening the study's reliability despite potential limitations @specia.

@@

An additional online survey aimed to delve deeper into these communication dynamics, highlights the fact that discussions about women working outside the home among male friends and relatives are infrequent. This lack of discourse correlates with larger gaps in perception versus reality, suggesting that minimal conversation contributes to widespread misperceptions. This correlation might also suggest a reverse causality, where the anticipation of conservative backlash inhibits open discussions, perpetuating a cycle of pluralistic ignorance @pluralistic. The lack of communication may not be entirely mass media’s failure to properly portray societal beliefs. When questioned, nearly 38% of participants very rarely discuss WWOH among their male friend circles. As shown in @fig-diss, the topic of WWOH is not very readily discussed among peers and colleagues. We hypothesize that this behaviour will extend onto social media, further supporting the idea that the perceived lack of support for WWOH is exacerbated by simply a deficiency in attention.

## Demographics
Straying from Burzstyn, Gonzalez, and Yanagizawa-Drott’s original analysis, we delve further into how demographical differences may or may not affect participants’ support for WWOH. We hypothesized that higher levels of education may correlate with increased rates of WWOH support. As shown in Figure 3 a and b,  there is a noticeable increase in percentage of individuals who oppose WWOH among Bachelor degree’s. However, this may be attributed to the lesser number of participant’s at any other education level. Overall, although there is a noticeable difference, the lack of participants at higher education levels makes it difficult to draw any significant conclusions about the correlation between education level and support for WWOH. We initially believed that higher levels of education may indicate more progressive beliefs due to increased likelihood of exposure to Western literature but more testing is required to draw any concrete results.

When separated into age groups, it appears that 18-23 year olds have the highest rate of WWOH opposition. This was shocking as we expected the younger generation with more exposure to social media and international communication to have the lowest rate of WWOH opposition. From @fig-age, we see that as the age groups get larger, so does the proportional support for WWOH. Similarly to when we separated the participants by education, we run into the issue of varying numbers of participants for each bin. 30-35 year old participants compose roughly a third of the number of 18-23 year olds making us skeptical about any conclusions drawn.

@@

When we split the participants into separate demographics, we found surprising trends. Categories that we believed would be more progressive actually turned out to have the highest rate of WWOH opposition. However, as shown in Figures 3 and 4, there is a disproportionate number of participants in each bin. Especially for higher education levels, the minimal number of participants with higher levels of education make it difficult to draw any correlation between education level and WWOH support. An avenue for further research may be to stratify the research sample with a big enough number of participants so that a better correlation can be shown.
